Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
comment on citing McAdams for similarity judgments

@@

\vl{On the two definitions of timbre, cite:
 Castellengo, M and D Dubois (2007). ?Timbre ou timbres? Propriété
du signal, de l?instrument, ou construction cognitive?? In: Cahiers
de la Société québécoise de recherche en musique 9, pp. 25?38
#biblio}

>>>>

\vl{On pairwise similarity judgments of timbre, cite:
McAdams, S et al. (1995). Perceptual scaling of synthesized musical
timbres: common dimensions, specificities, and latent subject
classes. In: Psychological research 58.3, pp. 177?192}

@@

\vl{On the two definitions of timbre, cite:
 Castellengo, M and D Dubois (2007). Timbre ou timbres? Propriété
du signal, de l?instrument, ou construction cognitive? In: Cahiers
de la Société québécoise de recherche en musique 9, pp. 25?38
#biblio}
